\LevelOne{afk}

\LevelTwo{Purpose}
This module provides afk detection, afk event, afk name customization and afk effects.

\LevelTwo{How it works?}
For each player, we have an \ttt{input counter} to track the last input time.\\
An input is as allows: mine blocks, movement.\\
The \ttt{afk checker} defined by cron will run and compare 2 consecutive value of the \ttt{input counter} associated with the player, if it's the same, then the player is considered as in afk.\\
In other words, if the \ttt{afk checker} is defined to run every 5 minutes, a player flagged as in afk is actually no input for 5--10 minutes.

\LevelTwo{Command}
\LevelThree{/afk}

\LevelTwo{Configuration}
\begin{Configuration}
    \item[format]{The \tbf{tab list name} format when a player is afk}

    \item[afk\_checker]{
        \begin{NestedList}
            \item[]
            \item[cron]{The cron to define how the afk\_checker is triggered.}
        \end{NestedList}

    }

    \item[afk\_event]{
        Execute commands on afk events.
        \begin{example}{Kick a player if he enters afk state}
            \begin{json}
                "on_enter_afk": [
                "send-broadcast <gold>Player %player:name% is now afk",
                "kick %player:name% You are kicked beacause of afk."
                ]
            \end{json}
        \end{example}
    }


    \item[event]{
        Afk effects are applied if a player enters afk state.

        \begin{NestedList}
            \item[invulnerable]{
                Immune to all damage?
            }

            \item[targetable]{
                Can be targeted by a hostile entity?
            }

            \item[moveable]{
                Can be moved if in afk state?
            }

        \end{NestedList}
    }

\end{Configuration}













