\LevelOne{works}

\LevelTwo{Purpose}
This module provides a bill-board gui for players to show their \tbf{works}.

\LevelTwo{Concept}
A \tbf{work} is a \tbf{teleporation point}. \\
\\
The types of work are as follows:
\begin{description}
    \item [Non-Production-Work] the project don't produce any resource (\eg bone, string, coal).
    \item[Production-Work] the project produce some resource.
\end{description}

\begin{note}{The main difference between non-production work and production-work}
    For a production-work, fuji provides the \ttt{production sample} to count the \ttt{hopper} and \ttt{minecart-hopper}
\end{note}

\begin{tips}{About the production counter}
    \begin{enumerate}
        \item You can use the production counter provided by production work to sample the output.
        \item {This module works with carpet-fabric's hopper counter. You can use both of them at the same time.}
        \item The hopper counter provided by this module will not destroy the item.
    \end{enumerate}

\end{tips}

\LevelTwo{Command}
\begin{enumerate}
    \item /works
\end{enumerate}

\LevelTwo{Configuration}
\begin{Configuration}
    \item[sample\_time\_ms]{
        For a production-work, how long should we sample it?
    }
    \item[sample\_distance\_limit]{
        For a production-work, how large the radius should we considered as the work's production.
    }
    \item[sample\_counter\_top\_n]{
        For a production-work, we only display the topN output items.
    }
\end{Configuration}








