\LevelOne{kit}
\LevelTwo{Purpose}
This module allows you to make kits.

\LevelTwo{Concept}
A \tbf{kit} is a set of itemstack.

\LevelTwo{Command}
\LevelThree{/kit editor}
Open the kit editor gui.

\LevelThree{/kit give}
Give a kit to a player.

\LevelTwo{Example}

\begin{example}{Create a kit}
    Use \ic{/kit editor} to create a kit.

    \begin{note}{The item slot position will keep}
        The item put inside the kit will keep its original position, so you can put armors in the right position.
    \end{note}

\end{example}

\begin{example}{Give a kit to a player}
    \ic{/kit give <player> <kit-name>}
    \begin{note}{The giving function behaviour}
        \begin{enumerate}
            \item {try to insert the item in the specified slot}
            \item {try to insert the item in any slot}
            \item {drop the item in the ground with the player as its thrower}
        \end{enumerate}
    \end{note}
\end{example}

\begin{example}{Associate a cooldown to a kit}
    To associate a cooldown with commands: see~\nameref{ch:command_cooldown}\\\\
    Create a \ttt{named cooldown} with 60sec cooldown and infinite usage: \ic{/command-cooldown create example-kit-cooldown 60000}\\\\
    Test the named cooldown, giving the kit to the player if the test is success:\ic{/command-cooldown test example-kit-cooldown <player> --onFailed "send-message \ph{player:name} wait a moment" kit give \ph{player:name} example-kit|send-message \ph{player:name} kit received.}\\\\

    Now, create a new command using~\nameref{ch:command_bundle} module to execute the test command
    \begin{example}{The config to create a new command for cooldown test command to give a kit if the test is success}
        \begin{json}
        {
            "requirement": {
            "level": 0,
            "string": null
        },
            "pattern": "claim-example-kit",
            "bundle": [
            "command-cooldown test example-kit-cooldown %player:name% --onFailed \"send-message %player:name% wait a moment (%fuji:command_cooldown_left_time example-kit-cooldown% ms)\" kit give %player:name% example-kit|send-message %player:name% kit received."
            ]
        }
        \end{json}
    \end{example}

\end{example}

\begin{example}{Claim a specific kit automatically for online players}
    You can use~\nameref{ch:command_scheduler} module to execute the \ic{/claim-example-kit} for online players automatically every minute.
\end{example}

\begin{example}{Give a kit to newbie player automatically}
    See~\nameref{ch:command_event}
\end{example}
